### 2014-11-05 Paper1/paper1.tex
Updated manuscript

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

@@

Attempts to deduce motor intent in the past have focused on the assumed spring-like properties of human muscles. Springs produce a force according to their impedance and stretch. By measuring force, impedance, and position, Gomi and Kawato\cite{gomi1997human} were able to deduce stretch and thereby infer the muscle's equilibrium point. Supporters of the ``$\lambda$ model''\cite{feldman1995origin} hypothesized that this equilibrium point represented the intent of a movement even though it did not consider mass as a feedforward controller would. Upon Gomi and Kawato's inspection of the equilibrium point as it evolved in time, it was clear that it was highly complex and often not anatomically realizable. Therefore, it could not well-represent the intent of a simple reaching movement. We propose a revised and more general method, \textit{intent extraction}, which calculates the intended trajectory even in the face of disturbances by relating environmental interaction and state to intent. This method affords new ways to 1) test and falsify candidate models of motor control, 2) study the timing and composition of alterations to intent during movement, and 3) understand how intent might be altered by pathology after neural insult. This method describes a class of filters that map a disturbance, process, actuator, and realized trajectory to an intended trajectory. In human reaching, these initial ingredients are available: the process is a dynamic model of the arm, the actuators (muscles) are assumed to act as viscoelastic torque generators, the human interface forces are measured by a sensor, and the realized trajectory is measured.

@@

\begin{table}[!ht]
\caption{
\bf{Arm Parameter Values and Sensitivities}}
\begin{tabular}{|c|c|c c|c c|}
\hline
Parameter Name &
Units &
Nominal &
SD &
$S$ &
$S_T$ \\ \hline
Upper Arm Length ($L_1$) &
m &
0.33 &
0.01 &
0 &
0.10 \\
Forearm Length ($L_2$) &
m &
0.34 &
0.01 &
0 &
0.03 \\
Upper Arm Center of Mass Ratio ($\frac{L_{m1}}{L_1}$) &
1 &
0.436 &
0.0695 &
0 &
0.02 \\
Forearm Center of Mass Ratio ($\frac{L_{m2}}{L_2}$) &
1 &
0.682 &
0.0431 &
0 &
0.02 \\
Gross Body Mass ($m_g$) &
kg &
79.36 &
3.1 &
0 &
0.02 \\
Upper Arm Mass Ratio ($\frac{m_1}{m_g}$) &
1 &
0.028 &
0.0029 &
0 &
0.01 \\
Forearm Mass Ratio ($\frac{m_2}{m_g}$) &
1 &
0.022 &
0.0025 &
0 &
0.06 \\
Upper Arm Radius of Gyration Ratio &
1 &
0.322 &
0.0161 &
0 &
0.01 \\
Forearm Radius of Gyration Ratio &
1 &
0.468 &
0.0234 &
0 &
0.01 \\
Shoulder Parallel Coordinate &
m &
-0.057 &
0.02 &
0.02 &
0.18 \\
Shoulder Perpendicular Coordinate &
m &
0.88 &
0.02 &
0 &
0.08 \\
Force Sensor Miscalibration $x\text{-axis}$ &
N &
0 &
0.231 &
0 &
0.08 \\
Force Sensor Miscalibration $y\text{-axis}$ &
N &
0 &
0.1067 &
0.03 &
0.08 \\
Force Sensor Gaussian Noise SD $x\text{-axis}$ &
N &
0 &
0.1653 &
0 &
0.01 \\
Force Sensor Gaussian Noise SD $y\text{-axis}$ &
N &
0 &
0.2869 &
0 &
0.01 \\
Torque-Invariant Impedance Misestimation Ratio &
1 &
1 &
0.15 &
0.06 &
0.31 \\
Torque-Varying Impedance Misestimation Ratio &
1 &
1 &
0.15 &
0 &
0.15 \\
Damping-to-Stiffness Ratio ($k_d$) &
$\text{sec}^{-1}$ &
0.0833 &
0.0125 &
0 &
0.08 \\
Reflex Impedance Scale Factor &
1 &
0.02 &
0.003 &
0 &
0.04 \\
Reflex Damping to Stiffness Ratio ($g_d$) &
$\text{sec}^{-1}$ &
2 &
0.3 &
0 &
0.04 \\ \hline
\end{tabular}
\begin{flushleft}Synthetic model parameters and their associated mean (nominal) values and standard deviations (SD) used to determine the sensitivity indices of Saltelli et al. \cite{saltelli2010variance}. Also shown are the resulting sensitivity indices. Sensitivity indices less than one-thousandth were reported as zero. Total variance was $1.3 \mu m^2$, showing very small average deviations when using this approach. First-order sensitivity, $S$, can be interpreted as fraction of variance removable by perfectly correcting a factor. Total sensitivity, $S_T$, can be interpreted as the fraction left after correcting all other factors.
\end{flushleft}
\label{tab:parameters}
\end{table}

>>>>

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphicsf
\usepackage{graphicx}

@@

Attempts to deduce motor intent in the past have focused on the assumed spring-like properties of human muscles. Springs produce a force according to their impedance and stretch. By measuring force, impedance, and position, Gomi and Kawato\cite{gomi1997human} were able to deduce stretch and thereby infer the muscle's equilibrium point. Supporters of the ``$\lambda$ model''\cite{feldman1995origin} hypothesized that this equilibrium point represented the intent of a movement even though it did not compensate for the dynamics of the arm as a feedforward controller would. Upon Gomi and Kawato's inspection of the equilibrium point as it evolved in time, it was clear that it was highly complex and often not anatomically realizable. Therefore, it could not well-represent the intent of a simple reaching movement. We propose a revised and more general method, \textit{intent extraction}, which calculates the intended trajectory even in the face of disturbances by relating environmental interaction and state to intent. This method affords new ways to 1) test and falsify candidate models of motor control, 2) study the timing and composition of alterations to intent during movement, and 3) understand how intent might be altered by pathology after neural insult. This method describes a class of filters that map a disturbance, process, actuator, and realized trajectory to an intended trajectory. In human reaching, these initial ingredients are available: the process is a dynamic model of the arm, the actuators (muscles) are assumed to act as viscoelastic torque generators, the human interface forces are measured by a sensor, and the realized trajectory is measured.

@@

\begin{table}[!ht]
\caption{
\bf{Arm Parameter Values and Sensitivities}}
\begin{tabular}{|c|c|c c|c c|c c|c|}
\hline
Parameter Name &
Units &
Nominal &
Source &
SD &
Source &
$S$ &
$S_T$ \\ \hline
Upper Arm Length ($L_1$) &
m &
0.33 &
TAM &
0.01 &
RM &
0 &
0.10 \\
Forearm Length ($L_2$) &
m &
0.34 &
TAM &
0.01 &
RM &
0 &
0.03 \\
Upper Arm Center of Mass Ratio ($\frac{L_{m1}}{L_1}$) &
1 &
0.436 &
\cite{winter2009biomechanics} &
0.0695 &
RM &
0 &
0.02 \\
Forearm Center of Mass Ratio ($\frac{L_{m2}}{L_2}$) &
1 &
0.682 &
\cite{winter2009biomechanics} &
0.0431 &
RM &
0 &
0.02 \\
Gross Body Mass ($m_g$) &
kg &
79.36 &
TAM &
3.1 &
\cite{stunkard1981accuracy} &
0 &
0.02 \\
Upper Arm Mass Ratio ($\frac{m_1}{m_g}$) &
1 &
0.028 &
\cite{winter2009biomechanics} &
0.0029 &
\cite{dempster1955space} &
0 &
0.01 \\
Forearm Mass Ratio ($\frac{m_2}{m_g}$) &
1 &
0.022 &
\cite{winter2009biomechanics} &
0.0025 &
\cite{dempster1955space} &
0 &
0.06 \\
Upper Arm Radius of Gyration Ratio &
1 &
0.322 &
\cite{winter2009biomechanics} &
0.0161 &
5\% &
0 &
0.01 \\
Forearm Radius of Gyration Ratio &
1 &
0.468 &
\cite{winter2009biomechanics} &
0.0234 &
5\% &
0 &
0.01 \\
Shoulder Parallel Coordinate &
m &
-0.057 &
RM &
0.02 &
RM &
0.02 &
0.18 \\
Shoulder Perpendicular Coordinate &
m &
0.88 &
RM &
0.02 &
RM &
0 &
0.08 \\
Force Sensor Miscalibration $x\text{-axis}$ &
N &
0 &
RM &
0.231 &
RM &
0 &
0.08 \\
Force Sensor Miscalibration $y\text{-axis}$ &
N &
0 &
RM &
0.1067 &
RM &
0.03 &
0.08 \\
Force Sensor Gaussian Noise SD $x\text{-axis}$ &
N &
0 &
RM &
0.1653 &
RM &
0 &
0.01 \\
Force Sensor Gaussian Noise SD $y\text{-axis}$ &
N &
0 &
MR &
0.2869 &
0 &
0.01 \\
Torque-Invariant Impedance Misestimation Ratio &
1 &
1 &
\cite{burdet2006stability} &
0.15 &
0.06 &
0.31 \\
Torque-Varying Impedance Misestimation Ratio &
1 &
1 &
\cite{burdet2006stability} &
0.15 &
0 &
0.15 \\
Damping-to-Stiffness Ratio ($k_d$) &
$\text{sec}^{-1}$ &
0.0833 &
\cite{burdet2006stability} &
0.0125 &
0 &
0.08 \\
Reflex Impedance Scale Factor &
1 &
0.02 &
\cite{burdet2006stability} &
0.003 &
0 &
0.04 \\
Reflex Damping to Stiffness Ratio ($g_d$) &
$\text{sec}^{-1}$ &
2 &
\cite{burdet2006stability} &
0.3 &
15\% &
0 &
0.04 \\ \hline
\end{tabular}
\begin{flushleft}Synthetic model parameters and their associated mean (nominal) values and standard deviations (SD) used to determine the sensitivity indices of Saltelli et al. \cite{saltelli2010variance}. Also shown are the resulting sensitivity indices. Sensitivity indices less than one-thousandth were reported as zero. Total variance was $1.3 \mu m^2$, showing very small average deviations when using this approach. First-order sensitivity, $S$, can be interpreted as fraction of variance removable by perfectly correcting a factor. Total sensitivity, $S_T$, can be interpreted as the fraction left after correcting all other factors. While most parameter values were available in the literature, some were chosen to correspond to a typical adult male (TAM), empirically through repeated measurements (RM), or as a percentage of the mean.
\end{flushleft}
\label{tab:parameters}
\end{table}
